\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\name{\bfseries{Ka Fai, Ng}} % Your name
\address{Room 3595, Academic Building, The Hong Kong University of Science and
Technology, Hong Kong}
\address{Email: kfngaa@connect.ust.hk; Tel: (852) 6018-2504 }
\address{Date of birth: 06-Nov-1990}
\address{Last updated: 10-Dec-2018}

\begin{document}

\begin{rSection}{Education}
\textit{Ph.D. in Civil Engineering} \hfill {Sep 2012 - Aug 2017}\\
Thesis: \textit{Sustainable Housing and Railway Developments over Space and Time}
\smallskip \\
Department of Civil and Environmental Engineering \\
The Hong Kong University of Science and Technology \\
\\
\textit{B.Eng in Civil and Structural Engineering} \hfill
{Sep 2009 - Aug 2012}\\
(First Class Honors, Academic Achievement Medal)\smallskip \\
Department of Civil and Environmental Engineering \\
The Hong Kong University of Science and Technology
\end{rSection}

\begin{rSection}{Experience}
\textit{Postdoctoral Researcher}{, Intelligent Transportation System Laboratory} \hfill {Sep 2017 -
Present}\\
The Hong Kong University of Science and Technology, Hong Kong\smallskip
\textit{Teaching Assistant}{, Intelligent Transportation System Laboratory} \hfill {Sep 2012 - Aug
2017}\\
The Hong Kong University of Science and Technology, Hong Kong\smallskip
\textit{Alumni Manager}{, School Manager, Incorporated Management Committee} \hfill {Jan
2015 - Aug 2018}\\
The Hong Kong Sheng Kung Hui Bishop Hall Secondary School, Hong Kong\smallskip
\textit{Full-time intern}{, Structural Group L} \hfill {Jun 2011 - Aug 2011}\\
Ove Arup and Partners Limited, Hong Kong\smallskip
\end{rSection}

\begin{rSection}{Research Interest}
\itemsep -5pt
\item Walkability and Sustainable Transport
\item Integrated Land Use and Transport Modeling and Planning
\item Infrastructure and Smart Cities development
\end{rSection}

\begin{rSection}{PUBLICATIONS}
\underline{Journal Publications}
\begin{enumerate}
\item \textbf{Ng, K.F.}, Lo, H.K., (2015). Optimal housing supply in a bid-rent
equilibrium framework. Transportation Research Part B: Methodological 74, 62-78.
\item \textbf{Ng, K.F.}, Lo, H.K., (2017). On joint railway and housing development:
Housing-led versus railway-led schemes. Transportation Research Part B: Methodological 106,
464-488.
\item \textbf{Ng, K.F.}, Lo, H.K., Huai Yue (2017). Robust public-private partnerships
for joint railway and property development. Frontier of Engineering Management 4(4), 437-450.
\end{enumerate}
\underline{Referred Conference papers}
\begin{enumerate}
\item \textbf{Ng, K.F.}, Lo, H.K., (2013). Optimal transport and land use patterns:
developer versus resident objectives. In: Proceedings of the 18th International Conference of
Hong Kong Society for Transportation Studies (HKSTS), Dec 2013.
\item \textbf{Ng, K.F.}, Lo, H.K., (2014). Optimal rail and housing development over
time. In: Proceedings of the 19th International Conference of Hong Kong Society for
Transportation Studies (HKSTS), Dec 2014.

\item \textbf{Ng, K.F.}, Lo, H.K., (2015). An option pricing-based evaluation of public-
private partnerships for joint railway and property development. In: Proceedings of the 20th

International Conference of Hong Kong Society for Transportation Studies (HKSTS), Dec 2015.
\item \textbf{Ng, K.F.}, Lo, H.K., (2016). Globally optimal housing supply under the
combined bid-rent model. In: Proceedings of the 21st International Conference of Hong Kong
Society for Transportation Studies (HKSTS), Dec 2016.
\item Huai, Yue, \textbf{Ng, K.F.}, Lo, H.K., (2017). Residential housing choice under
household compensatory decision. Proceedings of the 22nd International Conference of Hong
Kong Society for Transportation Studies (HKSTS), Dec 2017.
\item Huai, Yue, Lo, H.K., \textbf{Ng, K.F.}, (2018). The effects of activities allocation
on household compensatory decision in residential location choice. Proceedings of the 23rd
International Conference of Hong Kong Society for Transportation Studies (HKSTS), Dec 2018.

\end{enumerate}
\underline{Ongoing research paper}
\begin{itemize}
\item \textbf{Ng, K.F.}, Lo, H.K., Cen, Xuekai, (2018). A global optimal solution
algorithm to transportation network design problems. Working paper.
\item Cen Xuekai, \textbf{Ng, K.F.}, Lo, H.K., (2018). Optimal strategies for electric
vehicle promotion under mixed user equilibrium model. Working paper.
\item Huai, Yue, \textbf{Ng, K.F.}, Lo, H.K., (2018). Spatial distribution of activities
under bid-rent process and household compensatory decision mechanism. Working Paper.
\item \textbf {Ng, K.F.}, Lo H.K., Cen, Xuekai, Huang, Wei, (2018). User Equilibrium
Over Time in Reservation-based Transport Services with Users’ Priorities. Working Paper.
\end{itemize}
\end{rSection}

\begin{rSection}{Project Involvement}
\smallskip \underline{Granted}
\begin{itemize}
\item Strategies for Sustainable Railway Development over Time under Uncertainty.
General Research Fund 2016/17, HKUST16222216, Research Grants Council, The government
of Hong Kong Special Administrative Region, 1 January 2017 to 31 December 2019,
HKD\$482,605, 20. PI: Prof. Hong K. Lo, HKUST.
\item Strategies for Enhancing Walkability in Hong Kong via Smart Policies. Strategic
Public Policy Research Funding Scheme, Policy Innovation and Co-ordination Office, The
Government of Hong Kong Special Administrative Region, 36 months, Mar 2018,
HKD\$3,500,000. PI: Prof. Hong K. Lo, HKUST.
\end{itemize}
\end{rSection}

\begin{rSection}{TEACHING}
\underline{Experience}: Teaching assistant in transportation and other courses (in HKUST).
Duties include weekly tutorial, holding office hours, course reviews, supervision of student
projects, handling lab session, preparation of quizzes, lab experiment and exam papers, grading
of assignment project report and exam papers:
\begin{itemize}
\itemsep -5pt
\item
Infrastructure Systems Engineering and Management (2nd year undergraduates from Civil
Engineering)
\item Introduction to Transportation Systems (3rd year undergraduates from Industrial
Engineering)
\item Traffic and Transportation Engineering (3rd year undergraduates from Civil
Engineering)
\item Transportation System Operations (4th year undergraduates from Civil
Engineering)
\item Urban Transportation Networks Analysis (Postgraduates from Civil Engineering)
\item Traffic Control Fundamentals (Postgraduates from Civil Engineering)
\item Surveying and Surveying Camp (1st year undergraduates from Civil Engineering)
\item Computer-Aid Drawing (2nd year undergraduates from Civil Engineering)
\end{itemize}
\underline{Courses completed:}
\begin{itemize}
\itemsep -5pt
\item Transportation related: Traffic Control Fundamental (A+), Traffic and
Transportation Engineering (A+), Urban Transportation Analysis (A), Transportation System
Operations (A), Travel Demand Analysis (A-)
\item Other selected courses: Network Optimization in Transportation Systems,
Microeconomic Analysis, Deterministic Models in Operations Research
\end{itemize}
\underline{Capabilities:}
\begin{itemize}
\itemsep -5pt
\item Transportation course (from undergraduate to postgraduate level): Transportation
Planning, Traffic Flow, Transport Network Modeling, Land Use and Transport Modeling,

Transport Economics, Traffic and Transportation Engineering
\item Linear and Nonlinear Programming, Microeconomics, Probability and Statistic,
Project Management and Finance
\end{itemize}
\end{rSection}

\begin{rSection}{STUDENT SUPERVISION}
The Hong Kong University of Science and Technology (14 Students)
\vspace{6pt}\\
\underline{Master Students (8 students):}
\begin{itemize}
\item 2017 - 2018, Xiaozhan GAO, Zhejun CAI, \textit{Household compensatory
decision making in a linear network.}
\item 2017 - 2018, Yiren WANG, \textit{The effects of link improvement, housing
supply, and wage on heterogeneous households.}
\item 2017 - 2018, Yukai NI, Qichao CHEN, \textit{The prediction of salary and rent, a
study in Hong Kong Island.}
\item 2015 - 2016, Yue HUAI, Hin Wah MOON and Yuyao JIANG, \textit{Application of
public-private partnerships in Tseung Kwan O line and property development.}
\end{itemize}
\underline{Final Year Undergraduate (6 students):}
\begin{itemize}
\item 2017 - 2018, Ka Yu LEUNG and Cheuk Hin LAI, \textit{Should additional housing
supply be located near workplace or remote area? –Analysis of the interactions among housing
area, transport network and job salary in East Kowloon.}
\item 2016 - 2017, Kuan Zian LEONG and Kevin LEE, \textit{Modeling the behavior of
landlord and tenant in sub-letting and rending sub-divided and undivided housing based on
Hong Kong housing market.}
\item 2015 - 2016, Tsz Hing LO and Ho Yuen TANG, \textit{Housing Development
Strategies along a Transport Corridor: Investor versus Resident Perspective.} \textbf{Student
Paper Award 2016}, The Chartered Institution of Highways and Transportation Hong Kong
Branch (CIHT HKB).
\end{itemize}
\end{rSection}
\begin{rSection}{AWARDS AND HONORS}
\begin{itemize}
\item 2018, Chinese Overseas Transportation Association (COTA) Best
Dissertation Competition, First Runner-up: Sustainable Housing and Railway Developments
over Space and Time.
\item 2012, The Chartered Institute of Highways and Transportation Hong
Kong Branch (CIHT HKB) Student Paper Award 2012: Transportation Management Strategies
for Emissions Reduction.
\item 2012, The University of Science and Technology, B.Eng in Civil and
Structural Engineering, First Class Honors and Academic Achievement Medal.
\end{itemize}
\end{rSection}

\begin{rSection}{PRESENTATION}

\underline{Conference:}
\begin{itemize} \itemsep -3pt
\item The 22nd International Conference of Hong Kong Society for Transportation
Studies (HKSTS), Hong Kong, Dec 2017. Topic: \textit{Public-Private Partnership
Configurations in Joint Railway and Property Development under Project Uncertainties.}
\item Frontier Forum on Road and Railway Traffic and Transportation Engineering
Management, Beijing Jiaotong University, Beijing, Nov 2017. Topic: \textit{Robust
public-private partnerships for joint railway and property development.}
\item The 21st International Conference of Hong Kong Society for Transportation
Studies (HKSTS), Hong Kong, Dec 2016. Topic: \textit{Globally optimal housing supply under
the combined bid-rent model.}
\item The 29th KKHTCNN symposium on Civil Engineering, Hong Kong, Dec 2016.
Topic: \textit{Assessing Public-Private Partnership in Railway and Property Development.}
\item The 3rd Cross-Strait Forum on Smart Rail Development – Present \& Future,
Hong Kong, Mar 2016. Topic: \textit{Assessing Public-Private Partnership in Joint Railway and
Property Projects.}
\item The 20th International Conference of Hong Kong Society for Transportation
Studies (HKSTS), Hong Kong, Dec 2015. Topic: \textit{An option pricing-based evaluation of
public-private partnerships for joint railway and property development.}
\item Conference on Advanced systems in Public Transport (CASPT), Rotterdam,
Netherlands, July 2015. Topic: \textit{Analyzing Public-Private Partnerships in Railway and
Property Development via Real Options.}
\item The 19th International Conference of Hong Kong Society for Transportation
Studies (HKSTS), Hong Kong, Dec 2014. Topic: \textit{Optimal rail and housing development
over time.}
\item The 18th International Conference of Hong Kong Society for Transportation
Studies (HKSTS), Hong Kong, Dec 2013. Topic: \textit{Optimal Transport and Land Use
Patterns: Developer versus Resident Objectives.}
\end{itemize}
\underline{Seminars and others:}
• \begin{itemize} \itemsep -3pt
\item Research Semainr, HKUST-Beihang University Joint Workshop on Transportation
Science, Hong Kong University of Science and Technology, Hong Kong, Dec 2017. Topic:
\textit{A global optimal solution algorithm to transportation network design problems.}
\item Ph.D. Thesis Defense, Department of Civil and Environmental Engineering, Hong
Kong University of Science and Technology, Aug 2017. Topic: \textit{Sustainable Housing and
Railway Developments over Space and Time.}
\item Research Seminar, Mainland-Hong Kong Joint Workshop on Transportation
Science, School of economics and management, Beijing University of Aeronautics and
Astronautics, Beijing, July 2016. Topic: \textit{Public and Private Partnership in Joint Railway
and Property Development.}
\item Department Seminar, Department of Civil and Environmental Engineering, Hong
Kong University of Science and Technology, Nov 2015. Topic: \textit{Analyzing Public-Private
Partnerships in Railway and Property Development via Real Options.}
\item Ph.D. qualifying examination, Department of Civil and Environmental
Engineering, Hong Kong University of Science and Technology, May 2015. Topic:
\textit{Integrated Land Use and Transport Planning and Public-Private Partnership.}
\item Department Seminar, Department of Civil and Environmental Engineering, Hong
Kong University of Science and Technology, May 2015. Topic: \textit{Optimal Rail and Housing
Development Over Time.}
\end{itemize}
\end{rSection}

\begin{rSection}{ACADEMIC SERVICE AND MEMBERSHIP}
Reviewer, Transportation Research Part B \\
Reviewer, Transportmetrica B: Transport Dynamics\\
Reviewer, Journal of Transportation Engineering, Part A: Systems\\
Reviewer, IEEE Transactions on Cybernetics\\
\end{rSection}
\begin{rSection}{COURSE OR FINAL PROJECTS}
in The Hong Kong University of Science and Technology (HKUST)
\begin{itemize}\itemsep -3pt
\item \textit{Signal Optimization of Two Intersections on Po Fung Road in Hong Kong}\\
Course: CIVL5630 Traffic Control Fundamentals, SPRING 2014
\item \textit{Evaluate Current Situation of Crossing Harbor Tunnels in Hong Kong} \\
Course: IELM5570 Network Optimization in Transportation Systems, FALL2012
\item \textit{Optimal Network Design under Budget Constraint}
\\Course: CIVL5610 Urban Transportation Network Analysis, FALL 2011
\item \textit{Transportation Management Strategies for Emissions Reduction}
\\ Course: Final year project, B.Eng. in Civil and Structural Engineering,
SPRING 2012.
\end{itemize}
\end{rSection}

\begin{rSection}{Referees}
\textbf{Hong Kam, Lo} (Supervisor)
\\
Chair Professor, Head of Civil and Environmental Engineering
\\
The Hong Kong University of Science and Technology\\
Clear Water Bay, Kowloon, Hong Kong
\\
Editor-in-chief, Transportmetrica B: Transport Dynamics
\smallskip \\
Contact:
\\
Tel: (852) 2358-8742, Fax: (852) 2358-1534
\\
Office: Room 3578 (via lift 27/28)
\\
Email: cehklo@ust.hk
\\
\textbf{Hai, Yang} \\
Chair Professor, Department of Civil and Environmental Engineering
\\
The Hong Kong University of Science and Technology
\\
Clear Water Bay, Kowloon, Hong Kong
\\
Editor-in-Chief, Transportation Research Part B: Methodological
\smallskip \\
Contact:
\\

Tel: (852) 2358-7178; Fax: (852) 2358-1534
\\
Office: Room 3597 (via lift 27/28)
\\
Email: cehyang@ust.hk
\\
\textbf{David Zhiwei, Wang}
\\
Associate Professor, School of Civil and Environmental Engineering
\\
Nanyang Technological University
\\
Main Campus, 50 Nanyang Avenue, Singapore 639798
\\
Associate Editor, Transportmetrica A: Transport Science \smallskip
\\
Contact:
\\
Tel: (65) 6790-5281
\\
Office: N1-01c-75
\\
Email: wangzhiwei@ntu.edu.sg
\\

\end{rSection}

\end{document}